\bf Are you normal? A new projection pursuit index to assess a sample against a multivariate null distribution

### 2024-07-03 paper.qmd
note to add the other outlyingness llit
adding in citations

Linear projections are useful in many aspects of statistical analysis of multivariate data, and especially useful for visualising the data. A linear projection provides a dimension reduction while maintaining interpretability. For example, a biplot (REF) shows the structure creating the maximum variance in the data, and also visualizing the projection matrix to learn which variables contribute to it. We might find clusters of outliers that were hiding in high dimensions.

More generally, projection pursuit (REF) defines a quantitative criterion for the interestingness of a projection (a projection pursuit index), and searches the space of possible projections for the most interesting one to display. We can also define sequences of interpolated linear projections to better understand a multivariate distribution. Animating a randomly selected interpolated sequence of linear projections is called a grand tour (REF). The combination of these two approaches would then use a projection pursuit index to select interesting projections, but display them via an interpolated path to provide context. This is called a guided tour (@cook1995).

@@

>>>>

Linear projections are useful in many aspects of statistical analysis of multivariate data, and especially useful for visualising the data. A linear projection provides a dimension reduction while maintaining interpretability. For example, a biplot [@Ga71;@GH96] shows the structure creating the maximum variance in the data, and also visualizing the projection matrix to learn which variables contribute to it. We might find clusters of outliers that were hiding in high dimensions.

More generally, projection pursuit [@FT74;@JS87;@Hu85] defines a quantitative criterion for the interestingness of a projection (a projection pursuit index), and searches the space of possible projections for the most interesting one to display. We can also define sequences of interpolated linear projections to better understand a multivariate distribution. Animating a randomly selected interpolated sequence of linear projections is called a grand tour [@As85;@BA86b;@BCAH05;@CLBW06;@tours2022]. The combination of these two approaches would then use a projection pursuit index to select interesting projections, but display them via an interpolated path to provide context. This is called a guided tour [@cook1995].

@@

Say something about the relationship with @directional-outlyingness and Stahel-Donoho outlyingness

### 2024-07-03 paper.tex
note to add the other outlyingness llit
adding in citations

Linear projections are useful in many aspects of statistical analysis of
multivariate data, and especially useful for visualising the data. A
linear projection provides a dimension reduction while maintaining
interpretability. For example, a biplot (REF) shows the structure
creating the maximum variance in the data, and also visualizing the
projection matrix to learn which variables contribute to it. We might
find clusters of outliers that were hiding in high dimensions.

More generally, projection pursuit (REF) defines a quantitative
criterion for the interestingness of a projection (a projection pursuit
index), and searches the space of possible projections for the most
interesting one to display. We can also define sequences of interpolated
linear projections to better understand a multivariate distribution.
Animating a randomly selected interpolated sequence of linear
projections is called a grand tour (REF). The combination of these two
approaches would then use a projection pursuit index to select
interesting projections, but display them via an interpolated path to
provide context. This is called a guided tour (\citet{cook1995}).

@@

\renewcommand\refname{Conclusion}
  \bibliography{bibliography.bib}

>>>>

Linear projections are useful in many aspects of statistical analysis of
multivariate data, and especially useful for visualising the data. A
linear projection provides a dimension reduction while maintaining
interpretability. For example, a biplot \citep{Ga71, GH96} shows the
structure creating the maximum variance in the data, and also
visualizing the projection matrix to learn which variables contribute to
it. We might find clusters of outliers that were hiding in high
dimensions.

More generally, projection pursuit \citep{FT74, JS87, Hu85} defines a
quantitative criterion for the interestingness of a projection (a
projection pursuit index), and searches the space of possible
projections for the most interesting one to display. We can also define
sequences of interpolated linear projections to better understand a
multivariate distribution. Animating a randomly selected interpolated
sequence of linear projections is called a grand tour
\citep{As85, BA86b, BCAH05, CLBW06, tours2022}. The combination of these
two approaches would then use a projection pursuit index to select
interesting projections, but display them via an interpolated path to
provide context. This is called a guided tour \citep{cook1995}.

@@

\section{Conclusion}\label{conclusion}

Say something about the relationship with
\citet{directional-outlyingness} and Stahel-Donoho outlyingness

  \bibliography{bibliography.bib}
